\subsection{Qualitative Reporting}

The qualitative reporting is an integrative part of the class in the form of blog post assignments ($1000\pm500$ words per post). Assignments have covered the following topics by chronological order to allow for progressive mutual sharing of experience on the class website\footnote{The full assignment descriptions can be found on the class website \cite{classweb2013}.} :

\begin{enumerate}
  \item {\bf First Contact with the Community} \\ 
This topic covers the motivations to choose a specific project as well as the process through which joining has occurred \cite{lakhani2005htu,robert2006,vonKrogh2012,}. Since the class organization (c.f. Section \ref{classmotivations}) set no constraints on which project could be chosen a broad variety of experiences where expected. Some reporting was expected on whether joining had been an informal process or a more formal established ``joining" script \cite{vonkrogh2003} and if this experience generalizes to all community joiners. We stress the importance of the joining process since a recent study has shown for Wikipedia how barriers to joining can endanger an open source project \cite{halfacker2013} \\

  \item {\bf Historical, Cultural and Demography Backgrounds} \\
Ideological, cultural and historical traits play a fundamental role in {\it sorting} communities. Evidence of this sorting has been brought regarding open source license types \cite{belenzon2009}. The evolution of an open source project and the condition under which it can be joined are path dependent. Deciding to join a project requires a good understanding of the cultural traits and social norms of the community. In this part, it was asked to report on the most relevant historical, cultural and demographic traits of joined projects and communities. \\


 \item{\bf Communication Infrastructure}\\
The success of open collaboration is deeply rooted in the capacity of community to organize with the help of online information systems (c.f. \cite{benkler2002} for theoretical argument), which in turn determine the way communities interact and keep records of the open collaboration innovation steps. \\

  \item {\bf Community Participation} \\
Blog post about community participation. Incorporate links to your project participation and engage the readings. Do they generalize to your experience? Or not? How? \\

  \item {\bf Governance \& Decision Process}\\
  One of toughest issue with large and rather horizontal communities is the decision process. The relevant question here is : How does a community make tough decisions? Open collaboration communities have shown some level creativity in that regard, with a large variety of governance models ranging from consensus ranging to benevolent dictatorship. The governance approach might be related to the project goals or simply be the result of path dependent history. Depending on the community, the governance structure can be informal or on the contrary clearly documented.

\end{enumerate}


\noindent Two blog posts (assignments) are due after the expected delivery date of this report so their analyses cannot be included here :

\begin{enumerate}[resume]
\item {\bf Funding Sources \& Business Model} \\
Most open collaboration projects having reached a sufficient momentum rely on funding. Funding sources are diverse and can determine how a project is likely to further develop. The funding issue is highly related with the business model and how it can make a difference with competing ventures (closed or open source).

\item{\bf Organization \& Project Modularity}\\
The ``mirror hypothesis" is a theory that community organization should reflect the technical modularity of a project \cite{maccormack2012}. We are investigating how ``both" modularities can affect project organization and the joining process.

\end{enumerate}


