\subsection{Survey}
\label{sec:survey}

To complement our qualitative understanding of open source software joining, we designed a survey {\it in collaboration} among class members. Overall, the questions reflected the course readings and the participants' experiences within their respective open source communities. \\

\noindent First, class participants generated questions in a lab session, with several participants incorporating additional questions remotely later on. The questions were then categorized by concept tags: Communication, Demographics, Joining, Infrastructure, Motivation, Governance, Contribution, Finance, Social Network and Educational Experiences. From there, an effort was made to format the survey's presentation and flow based on the categories, as well as reducing replication inquiries. Questions used in the survey  are presented in Appendix \ref{app:survey_form}. As the survey was intended for class-use only, the class participants did not pilot it before collecting responses. The final sample size was 24 responses, 100\% of the class.\\

\noindent In the review of the question and during the analysis phase, we found several flaws described in a separate paragraph (see section \ref{sec:limitations}). We believe these questions should be addressed better in the future; the current survey is a starting point and {\bf should be iteratively improved}. Some of the appropriate follow-up questions are included in this work. Furthermore, the collective design process ensured that most of questions were relevant to the majority, as can be seen in the following analysis part.