\section{Syllabus}

\begin{enumerate}
\item Course overview \\
Skim: 
\href{http://quaid.fedorapeople.org/TOS/Practical_Open_Source_Software_Exploration/html/}{Practical OSS Exploration: How to be Productively Lost, the Open
Source Way}
\item Collective Action, Incentives, and Performance Evaluation \\
Required :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Benkler, Y. The Penguin and the Leviathan: How Cooperation Triumphs
  over Self-Interest (Crown Business, 2011), 1 edn.
  \href{http://www.youtube.com/watch?v=dPbE3WieoUo}{video}
\item
  Gulley, N. \& Lakhani, K. R. The determinants of individual
  performance and collective value in Private-Collective software
  innovation. Social Science Research Network Working Paper Series
  (2010). \href{http://ssrn.com/abstract=1550352}{article}.
\item
  Pickard, G. et al. Time-Critical social mobilization. Science 334,
  509-512 (2011). \href{http://arxiv.org/abs/1008.3172}{preprint}
\item
  Dan Pink \href{http://www.youtube.com/watch?v=KgGhSOAtAyQ}{video}
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Benkler, Y. Coase's penguin, or, linux and ``the nature of the firm''.
  The Yale Law Journal 112, 369+ (2002).
  \href{http://dx.doi.org/10.2307/1562247}{link}.
\item
  Hess, C. \& Ostrom, E. Ideas, Artifacts, and Facilities: Information
  as a Common-Pool Resource. Law and Contemporary Problems 111-146
  (2003).
\item
  Cooper, S. et al. Predicting protein structures with a multiplayer
  online game. Nature 466, 756-760 (2010).
\item
  Ostrom, E. Governing the Commons: The Evolution of Institutions for
  Collective Action (Political Economy of Institutions and Decisions)
  (Cambridge University Press, 1990)
\end{itemize}
\item LAB: Github and Pull Requests
\item Technical Infrastructure and Community Etiquette 
\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Fogel, K. ``Technical Infrastructure'' Producing Open Source Software
  \href{http://producingoss.com/en/technical-infrastructure.html}{link}
\item
  Raymond, E. ``How to ask questions the smart way''
  \href{http://www.catb.org/esr/faqs/smart-questions.html}{link}
\item
  von Krogh, G., Spaeth, S. \& Lakhani, K. R. Community, joining, and
  specialization in open source software innovation: a case study.
  Research Policy 32, 1217-1241 (2003).
  \href{http://flosshub.org/system/files/rp-vonkroghspaethlakhani.pdf}{link}
\end{itemize}

\item IRC Field Trip

\item Social Networks, Human Timing, Triggering Dynamics, Emotions and Politeness \\

Required :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Leskovec, J., Huttenlocher, D. \& Kleinberg, J. Predicting positive
  and negative links in online social networks. In Proceedings of the
  19th international conference on World wide web, WWW '10, 641-650
  (ACM, New York, NY, USA, 2010).
  \href{http://arxiv.org/abs/1003.2429}{article}
\item
  Maillart, T., Sornette, D., Frei, S., Duebendorfer, T. \& Saichev, A.
  Quantification of deviations from rationality with heavy tails in
  human dynamics. Physical Review E 83, 056101+ (2011).
  \href{http://arxiv.org/abs/1007.4104}{preprint}
\item
  Crane, R. \& Sornette, D. Robust dynamic classes revealed by measuring
  the response function of a social system. Proceedings of the National
  Academy of Sciences 105, 15649-15653 (2008).
  \href{http://arxiv.org/abs/0803.2189}{preprint}
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Danescu-Niculescu-Mizil, C., Sudhof, M., Jurafsky, D., Leskovec, J. \&
  Potts, C. A computational approach to politeness with application to
  social factors. In Proceedings of ACL (2013).
  \href{http://www.mpi-sws.org/~cristian/Politeness.html}{link}
\item
  Mitrović, M., Paltoglou, G. \& Tadić, B. Networks and emotion-driven
  user communities at popular blogs. The European Physical Journal B -
  Condensed Matter and Complex Systems 77, 597-609 (2010).
  \href{http://link.springer.com/article/10.1140/epjb/e2010-00279-x}{article}
\item
  Granovetter, M. S. The strength of weak ties. American Journal of
  Sociology 78, 1360-1380 (1973).
  \href{http://sociology.stanford.edu/people/mgranovetter/documents/granstrengthweakties.pdf}{Article}
\end{itemize}

\item LAB: Hunting Social Epidemics \& Human Timing (Data exploration)

\item Intellectual and Institutional History \\

Required:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  ``Brief history of open source''
  \href{http://www.netc.org/openoptions/background/history.html}{link}
\item
  Stallman, R. ``Why Software Should Not Have Owners.''
  \href{http://www.gnu.org/philosophy/why-free.html}{link}
\item
  \href{http://www.ischool.berkeley.edu/newsandevents/news/20120216timoreilly}{O'Reilly,
  T.} ``The Architecture of Participation''
  \href{http://oreillynet.com/pub/wlg/3017}{link}.
\item
  (just the introduction) O'Reilly, T. ``Government as a Platform''
  \href{http://chimera.labs.oreilly.com/books/1234000000774/ch01.html}{link}
\item
  skim Newitz, A. ``I've Seen the Worst Memes of My Generation Destroyed
  by Madness''
  \href{http://io9.com/ive-seen-the-worst-memes-of-my-generation-destroyed-by-464948581}{link}
  (note comment by O'Reilly) about Morozov, E. ``The Meme Hustler''
  \href{http://www.thebaffler.com/past/the_meme_hustler}{link}
\item
  Froomkin, A. Michael. \emph{Read only Section II, pp.~777-795.}
  ``Habermas@Discourse. Net: Toward a Critical Theory of Cyberspace.''
  Harvard Law Review 116, no. 3 (January 2003): 749--873.
  \href{http://osaka.law.miami.edu/~froomkin/discourse/ils.pdf}{link}
\item
  Chapter 3, ``The Movement'', and Chapter 4, ``Sharing Source Code'',
  from Kelty, C. \emph{Two Bits}
  \href{http://twobits.net/pub/Kelty-TwoBits.pdf}{link}
\item
  Hill, B ``Mako''. ``When Free Software isn't (Practically) Better.''
  \href{http://media.libreplanet.org/u/libby/m/mako/}{video}
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Raymond, E. ``The cathedral and the bazaar.'' Knowledge, Technology \&
  Policy 12, 23-49 (1999).
  \href{http://www.catb.org/esr/writings/homesteading/}{link}
\item
  Raymond, E. ``A Brief History of Hackerdom.''
  \href{http://www.catb.org/esr/writings/cathedral-bazaar/hacker-history/}{link}
\item
  Levy, S. Hackers: Heroes of the Computer Revolution (O'Reilly, 2010),
  3rd edn.
\item
  Belenzon, S. \& Schankerman, M. A. Motivation and sorting in open
  source software innovation. Social Science Research Network Working
  Paper Series (2009). \href{http://ssrn.com/abstract=1401776}{working
  paper}.
\end{itemize}

\item Local Pelican Installation\\
Used as the course content management system.

\item Game Theory and The Evolution of Cooperation \\

Required :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Axelrod, R. The Evolution of Cooperation: Revised Edition (Basic
  Books, 2006), revised edn. : Chapter 2 : The Success of TIT FOR TAT in
  Computer Tournaments
  \href{http://jcr.sagepub.com/content/24/1/3.short}{article}, Chapter 3
  : The Chronology of Cooperation
  \href{http://www.jstor.org/stable/1961366}{article}
\item
  Gächter, S., von Krogh, G. \& Haefliger, S. Initiating
  private-collective innovation: The fragility of knowledge sharing.
  Research Policy 39, 893-906 (2010)
  \href{http://www.smi.ethz.ch/news/docs/GachtervonKroghHaefliger_ResPol2010.pdf}{article}
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Axelrod, R. The Evolution of Cooperation: Revised Edition (Basic
  Books, 2006), revised edn. (excerpts) : Chapter 5 :
  \href{http://www.sciencemag.org/content/211/4489/1390.short}{article}
\item
  Helbing, D. \& Yu, W. The outbreak of cooperation among success-driven
  individuals under noisy conditions. Proceedings of the National
  Academy of Sciences 106, 3680-3685 (2009).
\end{itemize}

\item Project governance\\

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  ``Apache Voting Process''
  \href{http://www.apache.org/foundation/voting.html}{link}
\item
  Fogel, K. ``Social and Political Infrastructure''
  \href{http://producingoss.com/en/social-infrastructure.html}{link}
\item
  Freeman, J. The ``Tyranny of Structurelessness''
  \href{http://www.jofreeman.com/joreen/tyranny.htm}{link}
\item
  Shah, S. K. Motivation, governance, and the viability of hybrid forms
  in open source software development. Manage. Sci. 52, 1000-1014
  (2006).
  \href{http://faculty.washington.edu/skshah/Shah\%20-\%20Motivation,\%20Governance,\%20Hybrid\%20Forms.pdf}{link}
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  ``Arrows Impossibility Theorem''
  \href{http://en.wikipedia.org/wiki/Arrow\%27s_impossibility_theorem}{link}
\end{itemize}

Example bylaws documents:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Apache Pig Bylaws
  \href{http://www.apache.org/foundation/voting.html}{link}
\item
  GeoServer Community Process
  \href{http://docs.geoserver.org/stable/en/developer/policies/community-process.html}{link}
\item
  Linux Bylaws \href{http://www.linuxfoundation.org/about/bylaws}{link}
\item
  Wikipedia Governance -
  \href{http://p2pfoundation.net/Wikipedia_-_Governance}{link}
\end{itemize}

\item Community Joining and Governance (in relation with the Class Collective Project)\\

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  von Krogh, G., Spaeth, S. \& Lakhani, K. R. Community, joining, and
  specialization in open source software innovation: a case study.
  Research Policy 32, 1217-1241 (2003).
  \href{http://flosshub.org/system/files/rp-vonkroghspaethlakhani.pdf}{link}
\item
  Tomlinson, B. et al. Massively distributed authorship of academic
  papers. In CHI '12 Extended Abstracts on Human Factors in Computing
  Systems, CHI EA '12, 11-20 (ACM, New York, NY, USA, 2012).
  \href{http://dx.doi.org/10.1145/2212776.2212779}{link}
\item
  O'Mahony, S. \& Ferraro, F. The emergence of governance in an open
  source community. Academy of Management Journal 50, 1079-1106 (2007).
  \href{http://dx.doi.org/10.5465/amj.2007.27169153}{link}
  \href{http://www.jstor.org/stable/20159914}{alternative link}
\end{itemize}

\item Money\\
\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Asay, M. ``Fitting the optimal level of openness to your business
  strategy''
  \href{http://news.cnet.com/8301-13505_3-10244853-16.html}{link}
\item
  Fogel, K. ``Money'' \href{http://producingoss.com/en/money.html}{link}
\item
  Kelty, C. ``Conceiving Open Systems'', only the sections
  \emph{Hopelessly Plural}, \emph{Open Systems One: Operating Systems},
  \emph{Figuring Out Goes Haywire}, \emph{Denuemont}.
  \href{http://www.jus.uio.no/sisu/two_bits.christopher_kelty/5.html}{link}
\item
  Pentaho. ``The Beekeeper''
  \href{http://wiki.pentaho.com/display/BEEKEEPER/The+Beekeeper}{link}
\item
  Polrid, ``How Does Mozilla Make Money and Stay Afloat?''
  \href{http://www.technobuffalo.com/2010/01/01/how-does-the-mozilla-foundation-make-money/}{link}
\item
  Preston-Werner, T. ``Open Source (Almost) Everything''
  \href{http://tom.preston-werner.com/2011/11/22/open-source-everything.html}{link}
\item
  Worstall, T. ``So Why Is Google Funding Its Own Competition In The
  Firefox OS?''
  \href{http://www.forbes.com/sites/timworstall/2013/01/22/so-why-is-google-funding-its-own-competition-in-the-firefox-os/}{link}
\item
  And don't forget
  Wordpress\ldots{}\href{http://thenextweb.com/insider/2013/03/05/automattic-introduces-wordpress-com-business-a-new-pricing-tier-with-unlimited-themes-storage-and-customer-support/}{link1}
  \href{http://allthingsd.com/20120425/automattic-grows-up-the-company-behind-wordpress-com-shares-revenue-numbers-and-hires-execs/}{link2}
\end{itemize}

Explore:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{https://www.bountysource.com/}{BountySource}
\item
  \href{https://www.gittip.com/}{Gittip}
\item
  \href{http://www.kickstarter.com/}{Kickstarter}
\item
  \href{https://snowdrift.coop/}{Snowdrift.coop}
\end{itemize}

\item Social Networks, Cooperation, and Group Performance

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Hanaki, N., Peterhansl, A., Dodds, P. S. \& Watts, D. J. Cooperation
  in evolving social networks. Management Science 53, 1036-1050 (2007)
  \href{http://mansci.journal.informs.org/content/53/7/1036.short}{article}.
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Fu, F., Hauert, C., Nowak, M. A. \& Wang, L. Reputation-based partner
  choice promotes cooperation in social networks. Physical Review E 78,
  026117+ (2008)
  \href{http://dx.doi.org/10.1103/physreve.78.026117}{article}.
\item
  Blundell, C., Heller, K. \& Beck, J. Modelling reciprocating
  relationships with hawkes processes. In Advances in Neural Information
  Processing Systems 25, 2609-2617 (2012)
  \href{www.gatsby.ucl.ac.uk/~ucgtcbl/papers/BluHelBec2012.pdf‎}{article}
\item
  Sparrowe, R. T., Liden, R. C., Wayne, S. J. \& Kraimer, M. L. Social
  networks and the performance of individuals and groups. Academy of
  Management Journal 44, 316-325 (2001)
  \href{http://www.jstor.org/stable/3069458}{article}
\item
  Zimmermann, M. G. \& Egu'iluz, V. M. Cooperation, social networks, and
  the emergence of leadership in a prisoner's dilemma with adaptive
  local interactions. Physical Review E 72, 056118+ (2005)
  \href{http://dx.doi.org/10.1103/physreve.72.056118}{article}.
\item
  Apicella, C. L., Marlowe, F. W., Fowler, J. H. \& Christakis, N. A.
  Social networks and cooperation in hunter-gatherers. Nature 481,
  497-501 (2012) \href{http://dx.doi.org/10.1038/nature10736}{article}
\item
  Woolley, A. W., Chabris, C. F., Pentland, A., Hashmi, N. \& Malone, T.
  W. Evidence for a collective intelligence factor in the performance of
  human groups. Science 330, 686-688 (2010).
  \href{http://dx.doi.org/10.1126/science.1193147}{article}.
\end{itemize}

\item Designing Organizations for Productive Bursts\\

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Georg von Krogh, Thomas Maillart, Stefan Haefliger, Didier Sornette,
  Designing Organizations for Productive Bursts (under review) 2013.
  (manuscript will be sent on the mailing list)
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  von Krogh, G., Haefliger, S., Spaeth, S. \& Wallin, M. W. Carrots and
  rainbows: Motivation and social practice in open source software
  development. MIS Quarterly 36 (2012)
  \href{http://search.ebscohost.com/login.aspx?direct=true\&db=bth\&AN=74756698\&site=ehost-live}{paper}
\item
  Benkler, Y. Coase's penguin, or, linux and ``the nature of the firm''.
  The Yale Law Journal 112, 369+ (2002)
  \href{www.yale.edu/yalelj/112/BenklerWEB.pdf‎}{paper}.
\item
  Maillart et al., Superlinear Productivity in Open Source Software
  (manuscript will be sent on the mailing list)
\end{itemize}

\item Survey Validation and Launch

\item International collaboration / Practicum Updates 

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Dravis, P. ``Open Source Software: Perspectives for Development''
  \href{http://www.infodev.org/infodev-files/resource/InfodevDocuments_21.pdf}{link}
  Parts I and II.
\item
  Takhteyev, Y. and Hilts, A. ``Investigating the Geography of Open
  Source Software through Github''
  \href{http://www.takhteyev.org/papers/Takhteyev-Hilts-2010.pdf}{link}
\item
  Takhteyev, Y. pp.~94-147 (105-158 in the linkedPDF) ``1.2 The Global
  Tongue'' in \textbf{Coding Places: Uneven Globalization of Software
  Work in Rio de Janeiro, Brazil}
  \href{http://codingplaces.net/static/takhteyev_2009_dissertation.pdf}{link}
\end{itemize}

\item Survey Analysis

\item Economics and Management of Modularity

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Baldwin, C. Y. \& Clark, K. B. The architecture of participation: Does
  code architecture mitigate free riding in the open source development
  model? Manage. Sci. 52, 1116-1127 (2006)
  \href{http://mansci.journal.informs.org/content/52/7/1116.abstract}{paper}
\end{itemize}

Optional :
\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item MacCormack, A., Rusnak, J. \& Baldwin, C. Y. Exploring the
structure of complex software designs: An empirical study of open source
and proprietary code. Management Science 52, 1015-1030 (2006)
\href{http://pubsonline.informs.org/doi/abs/10.1287/mnsc.1060.0552}{paper}.
\item MacCormack, A., Baldwin, C. \& Rusnak, J. Exploring the duality
between product and organizational architectures: A test of the
``mirroring'' hypothesis. Research Policy 41, 1309-1324 (2012)
\href{http://dx.doi.org/10.1016/j.respol.2012.04.011}{paper}.
\item Maillart, T., Sornette, D., Spaeth, S. \& von Krogh, G. Empirical tests
of zipf's law mechanism in open source linux distribution. Physical
Review Letters 101, 218701+ (2008)
\href{http://prl.aps.org/abstract/PRL/v101/i21/e218701}{paper}. 
\item Simon,
H. The architecture of complexity. Proceeding of American Philosophy
Society 106, 467-482 (1962)
\href{http://www.jstor.org/discover/10.2307/985254}{paper}.
\item Gal, M. S.
Viral open source: Competition vs.~synergy. Journal of Competition Law
and Economics (2012)
\href{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=1978374}{paper}
\end{itemize}

\item Guest Lecture - Civic Hacking \textit{Sophia Parafina}

\item Human Timing and Economics of Attention

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Maillart, T., Sornette, D., Frei, S., Duebendorfer, T. \& Saichev, A.
  Quantification of deviations from rationality with heavy tails in
  human dynamics. Physical Review E 83, 056101+ (2011).
  \href{http://arxiv.org/abs/1007.4104}{preprint}
\end{itemize}

Optional :

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Barabási, A.-L. The origin of bursts and heavy tails in human
  dynamics. Nature 435, 207-211 (2005). URL
  http://dx.doi.org/10.1038/nature03459.
\end{itemize}

\item Guest Lecture - Project Teams in Community and Commercial Open Source Software Projects \textit{Tony Wasserman}

\item Guest Facilitator - Gender and Open Source \textit{Rochelle Terman}

\item Open Collaboration and Education; Class Wrap-up; Course Evaluations 

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Ellis, H.J.C., Morelli, R., de Lanerolle, T., Damon, J. and Raye, J.
  Can humanitarian open-source software development draw new students to
  CS? In Proceedings of the 38th SIGCSE Technical Symposium on Computer
  Science Education (Covington, Kentucky, USA), March 2007, pp.~551-555.
  \href{http://www.cs.trincoll.edu/hfoss/images/0/0a/Ellis_etal_SIGCSE_2007.pdf}{pdf}
\item
  Practical OSS Exploration. Forward.
  \href{http://teachingopensource.org/index.php?title=Practical_OSS_Exploration_-_Foreword\&direction=next\&oldid=3605}{link}
\item
  \href{http://www.hfoss.org/index.php/publications-etc}{see also}
\end{itemize}

\end{enumerate}