\subsection{Case Study: Experiences as a non-technical contributor on a technical open source project}
 
In the world of open source, attention is often focused on the coding aspect of the project and little focus is often given to the “non-technical” tasks that are required to keep a project smooth and accessible. On the particular project of MIFOS, an opensource micro-finance software, non-technical contributors are almost treated as second-tier contributors or afterthoughts. This can be seen simply by how non-technical contributors are received versus their technical counterparts. When one first navigates to their {\it How to contribute} page, the section greets you with a technology overview which guides one through the process of code submissions, coding standards, and commit privileges. There is no mention on the page of any alternative methods that one could contribute to the project. Only upon further digging and navigating through 2 more pages into the actual tasks list that are being requested can one find the non-technical tasks that are available for contributors.\\

\noindent While it is very understandable how software based projects would focus the majority of their attention on garnering focus toward coding based contributions, non-technical contributions should not be neglected. The very nature of open source is dependent on open adoption of their project. The foundation of OS was for the projects to be transparent and adoptable so that a community can easily grow around thrive around it. In the context of technical vs non-technical contributions, while technical contributions of coding adds to the core of what the project is, non-technical contributions help foster and grow the community to improve the front-end perceptions of the project as well as adoption accessibility. In a typical project, documentation and reporting is what helps newcomers acclimate to the new environment. Mailing lists help foster community and cohesion.\\

\noindent In most projects, contributors do not label themselves as technical or non-technical contributors. Technical contributors or coders also help documentation and contribute to mailing lists as well.  However, the infrastructure of the OS project may draw that line for them. In MIFOS, the code developers have their own mailing list. Suggestions from a non-code focused developer are submitted to the website instead of having them directly communicate over a forum. \\

\noindent Developers are further divided into task teams which further segregate the community. While this division may prove to increase efficiency by virtue of modularity, it also alienates members of the community and creates more ignorance or negligence of what needs to be done overall. From the results of the survey, we can see that almost a majority of respondents listed lack of clear documentation or mailing list activity as their response to what problems they encountered. More attention needs to be drawn to the non-technical aspect of Open Source projects in order to increase front-end fluidity and community cohesion.
