\mysubsubsection{Roles in the Community}
Fifty-nine percent of the survey respondents identified themselves as fulfilling more than one 
role within their communities. Of the 24 respondents, 41\% fulfilled one role; 30\% two roles; 21\% three roles; and 8\% for 4+ roles. 
The results illustrate collaborators not only wear different hats within the communities, but they possess additional skill sets suggesting the majority 
are willing to contribute across a variety of project tasks. Further study is needed to understand the reasons participants use multiple skill sets for their projects.\\

\noindent While a majority contributed more than one skill, most survey respondents identify as developers. Of the 24 survey responses, 25\% individuals function as Developers; 
18\% as User Experience Designers; 18\% as Documenters; 12\% as Testers; 10\% as Editors; 10\% as Other; and lastly, 8\% as Analysts. This suggests a majority of the participants contribute through software development 
within the community. Of the survey participants, the combined roles of Developer and User Experience Designer occurred most frequently. \\
 
\noindent The participants who categorized themselves as Other warrants additional follow-up questions in hopes of understanding any unidentified niche roles 
trending within the open source and peer collaboration space. Further study into the similarities and differences of each role within different types of open source 
communities may illicit a more nuanced picture.


