\mysubsubsection{Design and Previous Experiences}
In my experiences working on Hypothes.is for this class, a few questions had come to mind while I jumped into my first open source project. The first was trying to understand how difficult it would be for me to find a project that would suit my skills and what I'm looking for, since the only contribution I could really put forth was my design work. So some key quetsions that had arisen primarily involved how important design was to the project and what to expect from them. This tangentially led me to wonder how much experience others in the class had with open collaboration projects, since I felt that many had an easy time jumping into one or knowing what they wanted to do. I then felt like it was appropriate to ask the class these two pressing questions; "How important do you find design is to your project" and "what was your involvement with open source projects before this class". 

I was pleasantly surprised at the results I got. Many agreed that design was important to their project, with "I Agree" holding 61\% of the answers. I was more expecting a higher number of "I Somewhat Agree" which holds 35\% of the current answers. While I'm glad to know that many projects find design to be an important aspect of it, in hindsight I wonder if I should have rephrased the question to more analyze the role of the design team on the project. I felt like it was a given to understand that design is important, but it's another thing to actually see that the project actively prioritizes design by establishing an open collaborateive design team. 

The results for whether or not people had previous experience in open source projects did not surprise me, as many individuals seemed like they are generally active in this space. If anything I was slightly surprised by the number of "No" answers.

