\section{The survey form}
\label{app:survey_form}

What is your birth year?

Have you previously contributed to open source? Yes/No

Prior to this project, did you have any experience in the past with open source projects? (Free text)

Which of following best describes your project?
\begin{itemize}
\item Corporation lead open source project
\item Community originating open source project
\item Academic open source project
\item other (text form)
\end{itemize}
  
  
When was the project founded that you're contributing to? In other words, when were the initial contributions made to the project? (Free text)

How did you first hear about the project you eventually joined?
\begin{itemize}
\item direct human contact (friend, classmate, etc)
\item  brought up in class
\item article(blog, online periodical, etc)
\item mailinglist
\item print publication
\item web search
\item other: (text form)
\end{itemize}

Do you feel that branding matters to an open source project?
\begin{enumerate}
\item Yes
\item No
\item I don't know
\end{enumerate}

 Did the popularity of the project have an impact on your choosing to participate?
\begin{enumerate}
\item Yes
\item No
\item Undecided
\end{enumerate}

 Did you consider (but did not attempt to join) any other project before you joined your current one? If so, please identify the project(s), and the reason(s) why you did not choose them. (Free Text)

 Did you attempt to join any other project before you joined your current one? If so, please identify the project(s), and the outcome of your join attempt. (Free Text)

 Did you plan to join the project prior to this course? (Free Text)

\begin{enumerate}
\item  I was already a part of the project.
\item I intended to become a collaborator.
\item I found the project after joining the class.
\item other:
\end{enumerate}
 
Which technology/tool did you use for initial communication
\begin{enumerate}
\item IRC
\item Mailing List
\item Physical Meeting
\item Forum
\item Wiki
\item GitHub
\item Issue Tracker
\item Personal/Private Mail
\item Social Media (e.g. Facebook, Twitter)
\item Other:
\end{enumerate}

How long did you lurk before you contacted the community?
\begin{itemize}
\item 0 days
\item 1-3 days
\item 4-7 days
\item 8-14 days
\item 15-28 days
\item 29 days+
\item Not applicable 
\end{itemize}

If your project has "onboarding" info, please copy and paste the relevant text. (Free Text)

Does your project (in FAQ's or otherwise) have any join script or "onboarding" information for new people? (Free Text)

Which of the following orientation resources are available for your project?
\begin{enumerate}
\item General orientation/tutorial/FAQ material for newcomers
\item Designated person(s) or forum for newcomers to make first contact
\item Tasks or bugs tagged to be appropriate for newcomers to work on
\item Other:
\end{enumerate}

When joining your project, how many people replied to your initial communication? (Free Text)

Who reviewed / responded your initial contribution?
\begin{enumerate}
\item Project Founder
\item Senior Member
\item Newer Member
\item Unaffiliated commenter
\item No response
\item Other:
\end{enumerate}

Did the responses to your contribution read as from a:
\begin{enumerate}
\item Peer
\item Teacher
\item Boss
\item Deity 
\item Other:
\end{enumerate}

Describe the tone from others who responded to your initial contribution. (Free Text)

Which of the following aspects of a project was most important to you when choosing what to work on?
\begin{enumerate}
\item technical (state of the project, skills required, etc.)
\item community (norms, congeniality, preferred governance structure, etc.)
\item project goal (functionality, audience of product, etc.)
\item Other:
\end{enumerate}

Please elaborate on which aspect of a project was most important to you (technical, community, or project goal) in choosing what to work on. 

The following attributes are important to the open source project (5 points Likert)
\begin{enumerate}
\item Design
\item Performance
\item Documentation
\end{enumerate}

What role do you play within the open source community?
\begin{enumerate}
\item Developer
\item UX/Designer
\item Editor
\item Analyst
\item Tester
\item Documenter
\item Other:
\end{enumerate}

At what stage are you with your open source project currently?
\begin{enumerate}
\item My code/contribution is already in the project
\item Sent a pull request for review
\item Looking at the code/documents to contribute
\item Installating the project just sent an intro mail to the mailing list so far
\end{enumerate}

Was there a clear path to contributing to this project?
\begin{enumerate}
\item Yes, it was obvious what I needed to do.
\item Yes, but I had make an effort to figure it out.
\item No, it was somewhat murky.
\item No, I had no idea what to do or how to do it.
\end{enumerate}

How many hours per week on average do you spend contributing to the project?
\begin{enumerate}
\item 1 - 3 hours
\item 4 to 6 hours
\item 7 to 9 hours
\item 10+
\end{enumerate}

How many commits (contributions) have you made so far? (Free Text)

How many commits (contributions) do you think you will make in total by the end of the semester? (Free Text)

Did you have to learn new tools to participate in the project?
\begin{enumerate}
\item Yes
\item No
\end{enumerate}

What problems did you face with the project you are contributing to?
\begin{enumerate}
\item No response to my mail in the mailing list
\item Could not find proper documentation
\item Problems with the installation
\item Do not know how to use their version control system
\item Did not face any problems so far
\item Other:
\end{enumerate}

Give details related to the problems faced in your open source project. (Free Text)

How well is your project documented?
\begin{enumerate}
\item The documentation is robust and self-explanatory
\item There is active documentation but I have to sometimes ask the community for clarification
\item The documentation is sparse/the project is not documented
\end{enumerate}

Does your project have a FAQ?
\begin{enumerate}
\item Yes
\item No
\item Other:
\end{enumerate}

If your project has a FAQ, please give the URL. (Free Text)

What is the first thing you do when you face a problem or have a question about the project? Used mailing list to ask the question Used IRC Looked at mailing list archives Used Github Used forums Other: Does your project have equal amount of information for different roles to get started? Example roles: developers, testers, documenters... Yes No I don't know Not relevant Other: If you think that your project does not have equal amount of information for different roles, please explain why? (Free Text)

If you've learned new tools, what are they? (Free Text)

What are the version control tools used in your open source project?

\begin{enumerate}
\item Github
\item Bitbucket
\item SVN
\item Wiki
\item Other:
\end{enumerate}

If the project is using GitHub/other version control tool, write the main repository url. (Free Text)

What do you want to get in return for your contribution? Academic Publication Monetary Reward Experience in Open Source/Peer production Career Advancement Nothing at all Other: How many active contributors does the project have? (Free Text)

What is the percentage of females among active contributors (all kinds)? All kinds of contributors, not necessarily programmers. (Free Text)

\begin{enumerate}
\item  0-20 \%
\item 20-40 \%
\item 40-60 \%
\item 60-80 \%
\item 80-100 \%
\end{enumerate}

I don't know What is the degree of diversity (socioeconomic, racial, linguistic, tech knowledge, experience in FLOSS communities) in the community? "Not diverse at all" means most people share the same socioeconomic or racial background, language, or have similar tech backgrounds or amounts of experience in FLOSS communities. "Highly diverse" means there are significant differences among at least a large minority of active community members for these parameters. (5 point Likert)

\begin{enumerate}
\item Socioeconomic
\item Linguistic Racial/ethnic
\item Technical knowledge
\item Previous experience in FLOSS communities
\end{enumerate}

The diversity question is difficult to answer. Use this space to expand on kinds of diversity (or lack thereof) you've witnessed in your community.

How many people are on the "core team" if there is one? Use "other" to explain if there's not a core team.
\begin{enumerate}
\item 1
\item 2-3
\item 4-6
\item 6-10
\item 10+
\item Other:
\end{enumerate}

How many main committers are there that are not part of the "core team"? "Main committers" are defined as people who have made frequent contributions for more than 1 year. (Free Text)

Do you know the IRL identities of any of members of your project? If so, briefly profile a member of your project. What are her IRL interests, her job, etc? "IRL" = In Real Life. (Free Text)

Do you know other contributors personally outside of the project?
\begin{enumerate}
\item Yes
\item No
\end{enumerate}

If so, do you discuss your contributions with each other?
\begin{enumerate}
\item Yes
\item No
\end{enumerate}

What is the primary motivation for communication between members? (Check all that apply, but select primary motivations only)
\begin{enumerate}
\item Help/Advice
\item Social
\item Governance decisions
\item Notifications of changes or updates
\item Soliciting feedback
\item Other:
\end{enumerate}

Does the project have data available to map contributions/participation over time?
\begin{enumerate}
\item Yes - for the project as a whole
\item Yes - for the project as a whole and for individual sub-projects
\item No
\item Unknown
\item Other:
\end{enumerate}

How is the project funded? (check all that apply)
\begin{enumerate}
\item Venture backed (venture capital, angel investment, etc.)
\item Backed by corporation academic or research grants
\item Crowdfunded (i.e. through Kickstart campaign)
\item Bootstrapped by founders/core team
\item Donation based
\end{enumerate}

Does the project have anyone playing the role of a community manager?
\begin{enumerate}
\item Yes
\item No
\item Don't Know
\end{enumerate}

Does your community have any regularly scheduled meetings to engage its contributor community?
\begin{enumerate}
\item None
\item Weekly
\item Monthly
\item Quarterly
\item Other:
\end{enumerate}

Are contributors paid for their participation? If so, where does the money come from?
\begin{enumerate}
\item Unpaid
\item Paid as employees
\item Recieve money through grants
\item Project is sponsored Paid by donations
\item Crowed-funded
\item Other:
\end{enumerate}

What is the main license family used in the project?
\begin{enumerate}
\item GPL
\item BSD
\item MIT
\item Commercial dual licencing
\item Other:
\end{enumerate}

Would you still contribute to the project if it had a different license?
\begin{enumerate}
\item I only contribute to projects under copyleft licenses
\item I only contribute to free software (copyleft or permissive licenses)
\item My project is not under a free software license
\item I don't care / I don't know about licenses
\end{enumerate}

How is your project funded?
\begin{enumerate}
\item Grants (non-profits)
\item Grants (Federal)
\item Crowdsourced funding
\item Private/Corporate funding
\item No funded needed/in kind support
\item Other:
\end{enumerate}

What are the project's main expenses?
\begin{enumerate}
\item Paying contributors technical infrastructure (servers, etc.)
\item Promotional and marketing materials project
\item Does not have any major expenses
\end{enumerate}

What is the turnover rate in your community? Consider "leaving" as being active for at least 3 months and returning to inactive, meaning contributing less than 1 hour per month. (Free Text)

Expand on your answer in the question above about turnover. What have you observed in the community that led you to your answer? (Free Text)

Describe the management structure used in the project. (Free Text)

How would you describe the level of governance structuredness of your project ?
\begin{enumerate}
\item Tyranny of unstructuredness (no organization)
\item Self-organized (benevolent)
\item Dictatorship
\item Hierarchized community members edict the governance rules
\item Other:
\end{enumerate}

How does the community you are part of reach out to build awareness for the project? If applicable, comment on differences between reaching out to user and developer communities. (Free Text)

How long does it take to feel part of the community?

Describe your motivation to join the course. (Free Text)

The course delivered according to my motivation (5 point Likert).

What changes, if any, would you make to the course for the remainder of the semester? (Free Text)

What changes to the course, if any, would you make to the course, if it were taught again next semester? (Free Text)