\subsubsection{Discussion on Process}

One of the biggest hurdles that seem to come about the process of working on this survey and corresponding report primarily involves organization and clarity on responsibilities and roles. When having so many poeple contribute to a survey at once without any sort of restraint or control, there seems to have been a lot of redundant questions or questions that overlap with so many others. It was good that we ultimately chose someone to organize the content, but the process and the hurdles felt prolonged and slighly unorganized. Ultimately this does feel like it reflects an open source organization in the fact that there are mass amounts of contributions that required one benevolent dictator to organize and maintain quality control of the content. If it weren't for someone's intervention to organize the survey, it would have been much more of a chore to fill out and analyze. 

The final result of the survey came about easily enough. Google Survey assisted in making the results easy to digest and straightforward to discuss in a report. However, the discussion and exercises to understand what to do with this data in a report involved more discussion in a democratic way that once again, felt a little slow and a bit muddling. So many ideas and proposals on how to go about writing this report came up that it became easy to get lost about what direction everyone is actually taking. Once again I feel like this came about because there was a high emphasis on trying to get everyones input and thoughts in, leading to what felt like a really circular discussion. While I see the value in trying to get everyone's thoughts in the process, I felt as if there should be a stronger leading figure to ease along the final decision making process. 

The exercises in writing the modular parts of this paper were useful though, as well as the ultimate structure of how this report is written. Breaking off into groups to write one large paper, with each smaller group having a leadership figure to oversee the organization and writing process. This seems especially effective due to the fact that one large report can now be written with smaller parts contributed by everyone, and then organized by those responsible for each chapter. The only flaw I see in this is that it may possibly lead to a large paper that has stylistic inconsistencies or unorganized thoughts between chapters. The responsibility of going over the entire report and cleaning the content is a large role and hopefully can be done with ease. 