\mysubsubsection{FAQs and Onboarding Documentation}
Around 50\% of our projects have no actual FAQ or onboarding document, so an opportunity to help newcomers likely exists. Since only 8\% have an initial contact designated, there may be varying org structures, or a deliberate choice to have the entry point be distributed and in flux (according to needs). I do wonder if there could be some voluntary assignments. However, since members probably have forum or other contact points, presumably, newbies can take initiative and contact them.

I was exploring the qualitative potential of onboarding practices- text analysis may help (as well as some follow-up questions. Perhaps just raising the issue itself would capture attention of some project people.). Perhaps there is a connection between FAQ/onboarding info available and the org structure/governance of the actual projects.(Of course, the product and/or nature of the project is also relevant). My tentative summary:

Hypothesis: Development-centric (may be sufficient for their needs)
Peerlibrary: Ways to contribute are listed, described (Nice!). Hmm. Since Mitar wrote it, it may not be a coincidence that this is one of the best joining guides.
Mozilla PDF: Mentions all ideas are open (also, mainly bug, feature, and development-oriented)
Courtlistener: Great "ways to help" page
Facebook React: Developer and bug-centric, apologizes that easy flow for contribution is still being smoothed out (as well as transparency!)
Chromium: Developer-centric
Civi-CRM: no FAQ, but does express and embrace a  "just dive in" culture, which may be sufficient
Geonode: The about us page is a bit FAQ-like, with some info on getting started, contact, etc.
OaklandWiki(a site of the Localwiki project): it's a wiki which requires no login to contribute content. I actually added two sentences to the wiki with no account, so it was the easiest contribution I have ever made (No moderation?)
Mifos: Complex options: anyone can create an account. the ways to contribute are mainly technical, and some contribution screens require login, but I managed to find many volunteering options after digging into volunteer sections-- the site was a bit fragmented. Some confusion may arise from the availability of both "contributor" and "volunteer" sections and subsections. The technical and non-technical areas had various options and areas, and even more presumably available after creating a free account for login access.

OTHER PROJECTS: No FAQ/onboarding document (yet?)




