\mysubsubsection{Survey Design}


To complement our qualitative understanding, we designed a survey {\it in collaboration} among class members. Overall, the questions reflected the course  readings and the participants' experiences within their respective open source communities. 

First, class participants generated questions in a lab session, with several participants incorporating additional questions remotely later on.  Then, the questions were categorized by concept tags: Communication, Demographics, Joining, Infrastructure, Motivation, Governance, Contribution, Finance, Social Network and Educational Experiences. From there, a effort was made to format the survey's  presentation and flow, informed by the categories, as well as reduce replications inquiries.

Questions used in the survey  are presented in Appendix \ref{app:survey_form}. As the survey was intended for class-use only, the class participants did not pilot it before collecting  responses. The final sample size was 24 responses, nn \% of the class \todo{TODO: FIXME}.

In the review of the question and during the analysis phase, we found several flaws described in a separate paragraph (see section \ref{link_to_limitations}\todo{fixme}). We believe these questions can and should be developed further; the current survey is a starting point and {\bf should be iteratively improved}. Some of the appropriate follow-up questions are included in this work. Furthermore, the collective design process ensured that most of questions were relevant to the majority, as can be seen in the following analysis part.